UCD\\MSc Thesis Proposal:\\\emph{An approach for Continuous Capacity Planning in Cloud Environments with Uptime-based Pricing Model}

### 2015-04-11 paper/paper.tex
paper updates

\documentclass[]{final_report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{csvsimple}
\usepackage{float}
\usepackage[]{algorithm2e}
\usepackage{titlesec}
\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

@@

\chapter{Design}

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/cc2_8xlarge}
	\caption{\textit{cph} results for Amazon AWS cc2.8xlarge reserved instance for 1 year~\cite{AWS:2014}}
	\label{fig:cc2_8xlarge}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/cph_cc2_8xlarge_zoom}
	\caption{Zoomed \textit{cph} results for Amazon AWS cc2.8xlarge reserved instance for 1 year~\cite{AWS:2014}}
	\label{fig:cph_cc2_8xlarge_zoom}
\end{figure}

@@

\subsection{Data gathering, transformation and analytics}

@@

\subsubsection{Metrics collection}

        1,machine ID,INTEGER,YES

        2,start time,INTEGER,YES

        3,end time,INTEGER,YES

        4,duration INTEGER,YES

        5,sampled CPU usage,FLOAT,NO

        6,assigned memory usage,FLOAT,NO

        7,maximum memory usage,FLOAT,NO

        8,CPU capacity,FLOAT,YES

        9,Memory capacity,FLOAT,YES

\subsubsection{Daily metrics aggregation}

\paragraph{Calculate uptime per machine}
Input: Job start and end time logged for each machine in a form of \textless K, List\textless V\textgreater\textgreater

\paragraph{Aggregate CPU and memory usage}
Input: Sampled CPU and memory usage logged per job in a form of \textless K, List\textless V\textgreater\textgreater

\paragraph{Calculate number of jobs per day}
Input: Job id per machine \textless K, List\textless V\textgreater\textgreater

\paragraph{Calculate cluster averages for aggregations}
Input: Aggregated CPU, memory and number of tasks per machine per day \textless K, List\textless V\textgreater\textgreater

\paragraph{Calculate distance from optimality points based on uptime}
Input: Machine uptime per day

>>>>

\documentclass[]{final_report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{csvsimple}
\usepackage{float}
\usepackage[]{algorithm2e}
\usepackage{url}

\newcommand{\myparagraph}[1]{\paragraph{#1}\mbox{}\\}

@@

\chapter{Design and Implementation}

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/cc2_8xlarge}
	\caption{\textit{cph} results for Amazon AWS cc2.8xlarge reserved instance rented for 1 year~\cite{AWS:2014}}
	\label{fig:cc2_8xlarge}
\end{figure}

\begin{figure}[H]
	\includegraphics[width=\linewidth]{figures/cph_cc2_8xlarge_zoom}
	\caption{Zoomed \textit{cph} results for Amazon AWS cc2.8xlarge reserved instance rented for 1 year~\cite{AWS:2014}}
	\label{fig:cph_cc2_8xlarge_zoom}
\end{figure}

@@

\subsection{Prerequisites}

In order to make data-driven analysis and suggestions for optimization we need data. Below list of metrics was compiled based on algorithm needs to answer critical questions regarding state of infrastructure deployment. The list is suitable to guarantee performance SLOs only for compute nodes. Machines with significant I/O usage profile are not covered in this paper. 
Metrics can be gathered periodically, per process or per job. There are open source tools available to gather this data, e.g. collectd\footnote{\url{https://collectd.org}}, munin\footnote{\url{http://munin-monitoring.org}}, Logstash\footnote{\url{http://logstash.net}}.

\myparagraph{Machine Id}
A unique machine ID. Will be used as a key to compute further analytics.

\myparagraph{Start and End Time}
Timestamps to indicate start and end of measurement period.

\myparagraph{CPU usage}
Sampled or averaged CPU usage during measurement period.

\myparagraph{RAM usage}
Canonical memory usage measurement.

Metrics should be aggregated in \textless K, List\textless V\textgreater\textgreater format where K represents Machine Id and Vs are measurements.

\subsection{Metrics data transformations and analytics}

Metrics gathered in Prerequisites section have limited knowledge about an environment. Collection per job or per process produces one log line and is aware only about measurement period. Having such structured data would not let to answer machine wide neither cluster wide questions. The data has to be post-processed to allow calculation of below listed analytics.

\myparagraph{Uptime per machine}

\begin{algorithm}[H]
 \KwData{Task start and end time}
 \KwResult{Number of uptime hours per machine per day}
\end{algorithm}

Input: Job start and end time logged for each machine in a form of \textless K, List\textless V\textgreater\textgreater

\myparagraph{Aggregate CPU and memory usage}
Input: Sampled CPU and memory usage logged per job in a form of \textless K, List\textless V\textgreater\textgreater

\myparagraph{Calculate number of jobs per day}
Input: Job id per machine \textless K, List\textless V\textgreater\textgreater

\myparagraph{Calculate cluster averages for aggregations}
Input: Aggregated CPU, memory and number of tasks per machine per day \textless K, List\textless V\textgreater\textgreater

\myparagraph{Calculate distance from optimality points based on uptime}
Input: Machine uptime per day

@@
